Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2018-10-03 doc/network.tex
Autocommit (doc)

\begin{figure}
\includegraphics[width=\textwidth]{../fig/temporal_effect.pdf}
\caption{\textbf{Temporal varitaion in the mean observed generation interval.}
A deterministic Susceptible-Exposed-Infectious-Recovered (SEIR) model was simulated using Ebola-like parameters and the observed mean generation interval was calculated the course of an epidemic (see methods).
}
\label{fig:censor}
\end{figure}

@@

First, we compare how the estimates from the two methods vary across time using a single stochastic simulation on a homogeneous network (Figure~\ref{fig:example}).
During the initial exponential growth period (approximately between 9 and 20 weeks), both nonparametric and parametric methods yield similar estimates of mean generation interval and reproductive number.
Howeve, we observe opposite trends after the growth period (approximately after 20 weeks).
As the nonparametric method takes a weighted average of the observed distribution, increase in the observed mean generation interval leads to increase in the nonparametric estimates of both mean generation interval and reproductive number.
On the other hand, as the parametric method assumes a Poisson process with constant proportion of susceptibles, decrease in the number of susceptible results in underestimation of both mean generation interval and reproductive number.
we observe grdaual increase in the observed mean-generation interval as we aggregate more data, but the observed estimates always underestimate both mean generation interval and reproductive number, as predicted from the deterministic simulation.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{../fig/temporal_effect.pdf}
\caption{\textbf{Temporal variation in the mean observed generation interval.}
A deterministic Susceptible-Exposed-Infectious-Recovered (SEIR) model was simulated using Ebola-like parameters and the observed mean generation interval was calculated the course of an epidemic (see methods).
}
\label{fig:censor}
\end{figure}

@@

First, we compare how the estimates from the two methods vary across time using a single stochastic simulation on a homogeneous network (Figure~\ref{fig:example}).
During the initial exponential growth period (approximately between 9 and 20 weeks), both nonparametric and parametric methods yield similar estimates of mean generation interval and reproductive number.
However, we observe opposite trends after the growth period (approximately after 20 weeks).
As the nonparametric method takes a weighted average of the observed distribution, increase in the observed mean generation interval leads to increase in the nonparametric estimates of both mean generation interval and reproductive number.
On the other hand, as the parametric method assumes a Poisson process with constant proportion of susceptibles, decrease in the number of susceptible results in underestimation of both mean generation interval and reproductive number.
we observe grdaual increase in the observed mean-generation interval as we aggregate more data, but the observed estimates always underestimate both mean generation interval and reproductive number, as predicted from the deterministic simulation.
